---
title: "HW6"
author: "Chao Chen Yu"
date: "3/22/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(rvest)    
library(dplyr)    
library(tidyverse)   
library(repurrrsive)
```

1.
```{r}
movie100 = read_html("100.html" , encoding = "UTF-8" )
movie100 %>% html_nodes(".lister-item-header a") %>% html_text() -> Title
movie100 %>% html_nodes(".ipl-rating-star.small .ipl-rating-star__rating") %>% html_text() -> Ratings
movie100 %>% html_nodes(".runtime") %>% html_text() -> Runtime
Runtime <- as.numeric(gsub("min","",Runtime))

top100 = data.frame(Title, Ratings, Runtime)
head(top100)
```

2-a
List within another list either order list or unordered list is called nested list.
If a list A is the list item of another list B, then list A would be called a nested list.

2-b
```{r}
#listviewer::jsonedit(gh_repos)
```
There are six main lists in this data and in each main lists have 30 or 26 second sub-lists.
Also, in each second sub-list have 68 variables. Lastly, in some of variable also have some lists.

2-c
```{r}
repos <- tibble(repo = gh_repos)
repos
```
After running this code, we can see that there are six lists but, in each list there are still have some list.
So we still need to un-nest it.

2-d
```{r}
#listviewer::jsonedit(gh_repos)
```
As I mentioned above, the nested list configuration can let us to arrange the data methodically. 
Since sometime we will have the large amount data, so that we can use the nested list configuration to display the content 
neatly.

The 30 means that it's a first layer and 68 means that it's still have a second layer.
Go into the detailed configuration "rephos" data -> 6 lists -> 30 lists -> 68 variables -> list (some variable)


2-e
```{r}
tibble(repo = gh_repos) %>% 
  unnest_auto(repo) %>% 
  unnest_auto(repo)
```

